---
title: "Chi Square Test"
author: "Shashank Semwal"
date: "19 March 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(corrplot)
```

#A movie producer is bringing out a new movie. In order to map out a advertising campaign, he wants to determin wether the movie will appeal most to a particular age group or whether it will appeal equally to all age group. The producer takes a random sample from persons attending preview of the new movie and obtains the follwoing results.

```{r}

movie.df<-data.frame('Under 20'=c(146,54,20),'20-39'=c(78,22,10),'40-59'=c(48,42,10),'60 and Over'=c(28,22,20))
row.names(movie.df)<-c('Liked the Movie','Disliked the Movie','Indifferent')
movie.df
```


#Our Hypothesis
#H0 : Movies will not appeal any age group
#H1: Movies will appeal the age groups
#
# For X2 (Chi-Square) at 0.05 significance level i.e. 3.84

```{r}
# Chi square contigency Table
movies.chi<-chisq.test(as.matrix(movie.df))
```

```{r}
# Observed Values
movies.chi$observed

# Expected Values
movies.chi$expected


```

```{r}
# Age most constributing To likes, dislike aned indifferent about movies
corrplot(movies.chi$residuals,is.corr = F)

# we can see from the contribution table that 
# 1) People above age 60 are most indifferent about movies
# 2) People age b/w 40-50 mostly disliked the movie
# 3) Out of many people above age 60 dislked the movie
# 4) More people disliked the movie rather liked


```
```{r}
# For n=(3-1)(4-1)=6 for alpha=0.05, Chi-sq = 12.59

movies.chi

#we can see that p-value= 40.589, hence we reject the null hypothsis, Age group do affect the likes and dislikes about movies.
```



